---
title: "HardWork2/2"
author: "Cortland Watson"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    code_folding: hide
---

```{r, include=FALSE}
library(mosaic)
library(pander)
```


<script type="text/javascript">
 function showhide(id) {
    var e = document.getElementById(id);
    e.style.display = (e.style.display == 'block') ? 'none' : 'block';
 }
</script>


<hr />

# Reading {17}
<div style="padding-left:45px;">
| Section  | Points |
|----------|--------|
|     2.7  |     8    |      
| 2.8      |      4  |    
|    2.9   |       3  |
|       2.10|       2 |


</div>

<hr/>
<br/>


# Theory {5}

<!-- P R O B L E M     B E G I N S --> 

<div style="padding-left:45px;">
## Exercise 2.33

</div>

<div style="padding-left:60px;">

### <a href="javascript:showhide('Problem 2.33')">Problem 2.33</a>

<div id="Problem 2.33" style="display:none;">

In developing empirically a cost function from observed data on a complex chemical experiment, an analyst employed normal error regression model (2.1). $B_0$ was interpreted here as the cost of setting up the experiment. The analyst hypothesized that this cost should be $7.5 thousand and wished to test the hypothesis by means of a general linear test.

A) Indicate the alternative conclusions for the test.
B) Specify the full and reduced models.
C) Without additional information, can you tell what the quantity $df_R$ - $df_F$ in test statistic (2.70) will equal in the analyst's test? Explain.

</div>
</div>

<div style="padding-left:70px;">
<!-- Type Problem here -->

### Solution
<!-- Type Solution here -->

A) I do not know what this means....
B) Full = $B_0$ + $B_1$$X_i$ + $E_i$ Reduced = 7500 + $B_1$$X_i$ + $E_i$
C) $df_R$ - $df_F$ = 1 This is what happens when we have two parameters in the full model and just one in the reduced model, considering that we have $B_0$ set at $7.5 thousand.

</div>

<!-- P R O B L E M    E N D S -->



<!-- P R O B L E M     B E G I N S --> 

<div style="padding-left:45px;">
## Exercise 2.55
</div>

<div style="padding-left:60px;">

### <a href="javascript:showhide('Problem 2.55')">Problem 2.55</a>

<div id="Problem 2.55" style="display:none;">

Derive the expression for SSR in (2.51).

$SSR$ = $b^2_1$$\sum$($X_1$ - $\bar{X}$)^2

</div>
</div>

<div style="padding-left:70px;">
<!-- Type Problem here -->

### Solution
<!-- Type Solution here -->

$SSR$ = $b^2_1$$\sum$($X_1$ - $\bar{X}$)^2 

$\sqrt{SSR}$=$b_1$$\sum$($X_1$ - $\bar{X}$)

</div>

<!-- P R O B L E M    E N D S -->


<hr/>
<br/>


# Application {14}

<!-- P R O B L E M     B E G I N S --> 

<div style="padding-left:45px;">
## Exercise 2.25
</div>

<div style="padding-left:60px;">

### <a href="javascript:showhide('Problem 2.25')">Problem 2.25</a>

<div id="Problem 2.25" style="display:none;">

```{r, include=FALSE}
Ex2.25 <- read.table('http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR20.txt', header=FALSE)
```

Refer to AIRFREIGHT BREAKAGE problem 1.21.

A) Set up the ANOVA table. Which elements are additive?
B) Conduct an $F$ test to decide whether or not there is a linear association between the number of times a carton is transferred and the number of broken ampules; control the $\alpha$ risk at 0.05. State the alternatives, decision rule and conclusion.
C) Obtain the $t$ * statistic for the test in part (b) and demonstrate numerically its equivalence to the $F$ * statistic obtained in part (b).
D) Calculate $R^2$ and $r$. What proportion of the variation in $Y$ is accounted for by introducing $X$ into the regression model?

</div>
</div>

<div style="padding-left:70px;">
<!-- Type Problem here -->

### Solution
<!-- Type Solution here -->

```{r}
### Part A
# pander(summary(Ex2.25.lm))
# pander(anova(Ex2.25.lm))

### Part B
#$MSE$ = $SSE$/n-2
#$MSE$ = 3416/43 = 79.44186
#$MSR$ = $SSR$/1
#$MSR$ = 76960/1 = 76960
#$F$ * = $MSR$/$MSE$
#$F$ * = 76960/79.44186 = 968.7588

### Part C
#$t$ * = $\sqrt{$F$}$
#$t$ * = $\sqrt{968.7588}$ = 31.12

## Part D
# $R^2$ = $SSR$/$SSTO$
# $SSTO$ = $SSR$ + $SSE$
# $SSTO$ = 76960+3416 = 80376
# $R^2$ = 76960/80376 = 0.9574998
# $r$ = $\sqrt{$R^2$}$
# $r$ = sqrt(0.9574998) = 0.9785192
```

A) In the ANOVA table, the $df$ (1, 43) are additive. The $SSE$ (3416) and the $SSR$ (76960) are not additive.
B) I have not figured this one out yet
C) $t$ * = $\sqrt{968.7588}$ = 31.12
D) $R^2$ = 0.9574998  $r$ = 0.9785192

</div>

<!-- P R O B L E M    E N D S -->



<!-- P R O B L E M     B E G I N S --> 

<div style="padding-left:45px;">
## Exercise 2.26
</div>

<div style="padding-left:60px;">

### <a href="javascript:showhide('Problem 2.26')">Problem 2.26</a>

<div id="Problem 2.26" style="display:none;">

```{r, include=FALSE}
Ex2.26 <- read.table('http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR22.txt', header=FALSE)
```

Refer to PLASTIC HARDNESS problem (1.22).

A) Set up the ANOVA table.
B) Test by means of an $F$ test whether or not there is a linear association between the harness of the plastic and the elapsed time. Use $\alpha$ = 0.01. State the alternatives, decision rule, and conclusion.
C) Plot the deviations $Y_i$ - $\hat{Y}_i$ against $X_i$ on a graph. Plot the deviations $\hat{Y}_i$ - $\bar{Y}$ against $X_i$ on another graph, using the same scales as for the first graph. From your two graphs, does $SSE$ or $SSR$ appear to be the larger component of $SSTO$? What does this imply about the magnitude of $R^2$?
D) Calculate $R^2$ and $r$.

</div>
</div>

<div style="padding-left:70px;">
<!-- Type Problem here -->

### Solution
<!-- Type Solution here -->

A)
```{r}
Ex2.26.lm <- lm(V1 ~ V2, data=Ex2.26)
pander(anova(Ex2.26.lm))
```

B)I have not figured out how to do this one yet, or C)
C)
D) $R^2$= 0.9731 $r$= 0.9864583

</div>

<!-- P R O B L E M    E N D S -->



<!-- P R O B L E M     B E G I N S --> 

<div style="padding-left:45px;">
## Exercise 2.29
</div>

<div style="padding-left:60px;">

### <a href="javascript:showhide('Problem 2.29')">Problem 2.29</a>

<div id="Problem 2.29" style="display:none;">

```{r, include=FALSE}
Ex2.29 <- read.table('http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR27.txt', header=FALSE)
```


Refer to MUSCLE MASS problem (1.27).

A) Plot the deviations $Y_i$ - $\hat{Y}$ against $X_i$ on one graph. Plot the deviations $\hat{Y}$ - $\bar{Y}$ against $X_i$ on another graph, using the same scales as in the first graph. From your two graphs, does $SSE$ or $SSR$ appear to be the larger component of $SSTO$? What does this imply about the magnitude of $R^2$?
B) Set up the ANOVA table.
C) Test whether or not $B_1$ = 0 using an $F$ test with $\alpha$ = 0.05. State the alternatives, decision rule and conclusion.
D) What proportion of the total variation in muscle mass remains "unexplained" when age is introduced into the analysis? Is this proportion relatively small or large? 
E) Obtain $R^2$ and $r$.

</div>
</div>

<div style="padding-left:70px;">
<!-- Type Problem here -->

### Solution
<!-- Type Solution here -->

A)I do not know how to do this one
B)
```{r}
Ex2.29.lm <- lm(V1 ~ V2, data=Ex2.29)
pander(anova(Ex2.29.lm))
```

C) .7501 and this is pretty good depending on where you are studying, in psychology this is amazing, but in other sciences, we woudl like to see much better.
D) I do not know how to do this one either.
E) 0.7501=$R^2$ $r$=0.8660831

</div>

<!-- P R O B L E M    E N D S -->


</div>